Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
discretiZed

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
with full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into %\textcolor{red}{What is subscript ``d''?}
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the discretized matrices of $A$ and $B$, the plant dynamics. 
Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant) of interest.   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback, 
as implemented on modern FPGAs or ICs. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretised signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop digitalised dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
As argued later, in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature.

>>>>

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
with full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix) into %\textcolor{red}{What is subscript ``d''?}
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the discretized matrices of $A$ and $B$, the plant dynamics. 
Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant) of interest.   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback, 
as implemented on modern FPGAs or ICs. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop digitalised dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
As argued later, in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature.
